### 2014-02-15 paper/main.tex
update paper, minor edits

Assumption A2 can derived from (\ref{eqn:beta hat}) plus a couple of other assumptions. Specifically, assume that a) $\hat\beta_j, s_j$ contain most of the information about $\beta_j$ in the data $D_j$ (i.e. they are ``approximately sufficient" for $D_j$) and that b) $s_j$ alone contains little information about $\beta_j$. The former (a) suggests the approximation $\hat{L}_j(\beta_j) \propto p(\hat\beta_j, s_j | \beta) = p(\hat\beta | \beta, s_j) p(s_j | \beta)$, while the latter (b) suggests assuming that $p(s_j|\beta_j)$ does not depend on $\beta_j$. Putting these two together yields $\hat{L}_j(\beta_j) \propto p(\hat\beta_j | \beta, s_j)$, which, with (\ref{eqn:betahat}),  implies A2. If $\hat\beta_j, s_j$ are not sufficient for $D_j$ then there is some loss of efficiency in making this approximation, but all Bayesian inferences remain valid provided they are interpreted as conditional on $\hat\beta_j,s_j$, rather than conditional on $D_j$. See \cite{johnson.xx} and \cite{wakefield.xx} for more general discussion and examples of Bayesian inference based on summary statistics.

@@

While Assumption A2 has parallels with approaches like \cite{efron, cai?} that model the $Z$ scores $Z_j = \hat\beta_j/s_j$ as normally distributed under the null, 
there is an important difference: here, observations with a large $s_j$ have an essentially flat likelihood (\ref{eqn:lik}), and so do not affect inference for
other parameters, whereas when modeling the $Z$ scores directly, observations with large $s_j$ produce $N(0,1)$ $Z$ scores that do affect inference. In
this way the likelihood-based approach can take better account of the informativeness of each measurement, as illustrated in Results below.

@@

In practice, we implement the unimodal assumption (A1) by assuming a parametric finite mixture for $g$, 
\begin{equation} \label{eqn:g}
g(\cdot; \pi) = \pi_0 \delta_0(\cdot) + \sum_{k=1}^K \pi_k f_k(\cdot) 
\end{equation}
where $\delta_0(\cdot)$ denotes a point mass at 0, $\pi=(\pi_0,\dots,\pi_K)$ are mixture proportions to be estimated (with $\pi_j \geq 0, \sum_j \pi_j=1$), and $f_k$ are pre-specified 
component distributions with one of the following forms: 
\begin{enumerate}[i)]
\item $f_k(\cdot) = N(\cdot; 0, \sigma^2_k)$
\item $f_k(\cdot) = U[\cdot; -a_k,a_k]$
\item $f_k(\cdot) = U[\cdot; -a_k,0] \text{ or } U[\cdot; 0,a_k]$,
\end{enumerate}
where $N(\cdot; 0,\sigma^2)$ denotes the density of a normal distribution with mean 0 and variance $\sigma^2$ and
$U[\cdot; a,b]$ denotes the density of a uniform distribution on $[a,b]$.
That is, the non-zero effects are modeled as either i) a mixture of zero-centered normal distributions; ii) a mixture of zero-centered uniform distributions;
or iii) a mixture of ``zero-anchored" uniform distributions, which have one end of their range at 0. This approach closely mirrors approaches in \cite{campy.thomas}.

To see the flexibility of the representation (\ref{eqn:g})
think of $K$ as being ``large", with the values of $\sigma^2_k$ or $a_k$ 
spanning a wide range of values, from
essentially zero to unnecessarily large. In this way, as $K$ increases, the three different choices for $f_k$ can allow $g$ to approximate,
with arbitrary accuracy,
\begin{enumerate}[i)]
\item any scale mixture of normals, which includes as special cases
the double exponential (Laplace) distribution, any $t$ distribution, and a very large number of other distributions used in 
high-dimensional regression settings such as the spike and slab prior, the horseshoe prior \ref{}, or the more general three-parameter beta prior \ref{}.
\item any symmetric unimodal distribution about 0.
\item any (asymmetric) unimodal distribution about 0.
\end{enumerate}
The latter two claims are related to characterizations of unimodal distributions due to Khintchine (1938) and  Shepp (1962); see Feller, 1971, page  158. 
Furthermore, although it is natural for statisticians to immediately worry about ``overfitting" if $K$ is large, 
in fact the unimodal constraint is sufficient to prevent serious problems with overfitting. For example, note that the unimodal
constraint is sufficiently strong that there will exist a non-parametric
maximum likelihood estimate (NPMLE) for $g$ under this constraint. (Indeed, if the $\beta_j$ are observed without error, corresponding to the standard errors $s_j \rightarrow 0$, this NPMLE has an explicit and elegant form; \cite{grenander}.)
Thus allowing $K$ to be large in ii) or iii) can be thought of as approximating the NPMLE for $g$, under the constraints of symmetry and unimodality (ii), or unimodality alone (iii).

@@

Assuming independence across units, the likelihood for $\pi$ is 
\begin{equation}
L(\pi) := p(D_1,\dots,D_J | \pi) = \prod_{j=1}^n p(D_j | \pi)
= \prod_j \int p(D_j | \pi, \beta_j) p(\beta_j | \pi) d\beta_j \\
= \prod_j \int p(D_j | \beta_j) g(\beta_j; \pi) d\beta_j
\end{equation}

>>>>

Assumption A2 can derived from (\ref{eqn:betahat}) plus a couple of other assumptions. Specifically, assume that a) $\hat\beta_j, s_j$ contain most of the information about $\beta_j$ in the data $D_j$ (i.e. they are ``approximately sufficient" for $D_j$) and that b) $s_j$ alone contains little information about $\beta_j$. The former (a) suggests the approximation $\hat{L}_j(\beta_j) \propto p(\hat\beta_j, s_j | \beta) = p(\hat\beta | \beta, s_j) p(s_j | \beta)$, while the latter (b) suggests assuming that $p(s_j|\beta_j)$ does not depend on $\beta_j$. Putting these two together yields $\hat{L}_j(\beta_j) \propto p(\hat\beta_j | \beta, s_j)$, which, with (\ref{eqn:betahat}),  implies A2. If $\hat\beta_j, s_j$ are not sufficient for $D_j$ then there is some loss of efficiency in making this approximation, but all Bayesian inferences remain valid provided they are interpreted as conditional on $\hat\beta_j,s_j$, rather than conditional on $D_j$. See \cite{johnson.xx} and \cite{wakefield.xx} for more general discussion and examples of Bayesian inference based on summary statistics.

@@

While Assumption A2 has parallels with approaches like \cite{efron, cai?} that model the $Z$ scores $Z_j = \hat\beta_j/s_j$ as normally distributed under the null, 
there is an important difference: here, observations with a large $s_j$ have an essentially flat likelihood (\ref{eqn:lik}), and so do not affect inference for
other parameters, whereas when modeling the $Z$ scores directly, observations with large $s_j$ produce $Z$ scores with an $N(0,1)$ distribution that {\it do} affect inference. 
Because of this the likelihood-based approach can take better account of the informativeness of each measurement, as illustrated in Results below.

@@

In practice, we implement the unimodal assumption (A1) by assuming a parametric finite mixture for $g$, 
\begin{equation} \label{eqn:g}
g(\cdot; \pi) = \pi_0 \delta_0(\cdot) + \sum_{k=1}^K \pi_k f_k(\cdot) 
\end{equation}
where $\delta_0(\cdot)$ denotes a point mass at 0, $\pi=(\pi_0,\dots,\pi_K)$ are mixture proportions to be estimated (with $\pi_j \geq 0, \sum_j \pi_j=1$), and $f_k$ are pre-specified 
component distributions with one of the following forms: 
\begin{enumerate}[i)]
\item $f_k(\cdot) = N(\cdot; 0, \sigma^2_k)$
\item $f_k(\cdot) = U[\cdot; -a_k,a_k]$
\item $f_k(\cdot) = U[\cdot; -a_k,0] \text{ or } U[\cdot; 0,a_k]$,
\end{enumerate}
where $N(\cdot; 0,\sigma^2)$ denotes the density of a normal distribution with mean 0 and variance $\sigma^2$ and
$U[\cdot; a,b]$ denotes the density of a uniform distribution on $[a,b]$.
That is, the non-zero effects are modeled as either i) a mixture of zero-centered normal distributions; ii) a mixture of zero-centered uniform distributions;
or iii) a mixture of ``zero-anchored" uniform distributions, which have one end of their range at 0. These approaches closely mirror approaches in \cite{campy.thomas}.

To see the flexibility of the representation (\ref{eqn:g})
think of $K$ as being ``large", with the values of $\sigma^2_k$ or $a_k$ 
spanning a wide range of values, from
essentially zero to unnecessarily large. In this way, as $K$ increases, the three different choices for $f_k$ can allow $g$ to approximate,
with arbitrary accuracy,
\begin{enumerate}[i)]
\item any scale mixture of normals, which includes as special cases
the double exponential (Laplace) distribution, any $t$ distribution, and a very large number of other distributions used in 
high-dimensional regression settings such as the spike and slab prior, the horseshoe prior \ref{}, or the more general three-parameter beta prior \ref{}.
\item any symmetric unimodal distribution about 0.
\item any (asymmetric) unimodal distribution about 0.
\end{enumerate}
The latter two claims are related to characterizations of unimodal distributions due to Khintchine (1938) and  Shepp (1962); see Feller, 1971, page  158. 
Furthermore, although it is natural for statisticians to worry about ``overfitting" if $K$ is large, 
in fact the unimodal constraint is sufficient to prevent serious problems with overfitting. For example, note that the unimodal
constraint is sufficiently strong that there will exist a non-parametric
maximum likelihood estimate (NPMLE) for $g$ under this constraint. (Indeed, if the $\beta_j$ are observed without error, corresponding to the standard errors $s_j \rightarrow 0$, this NPMLE has an explicit and elegant form; \cite{grenander}.)
Thus allowing $K$ to be large in ii) or iii) can be thought of as approximating the NPMLE for $g$, under the constraints of symmetry and unimodality (ii), or unimodality alone (iii).

@@

Note; this needs some tidying.

Assuming independence across units, the likelihood for $\pi$ is 
\begin{align}
L(\pi) := p(D_1,\dots,D_J | \pi) = \prod_{j=1}^n p(D_j | \pi)
& = \prod_j \int p(D_j | \pi, \beta_j) p(\beta_j | \pi) d\beta_j \\
& = \prod_j \int p(D_j | \beta_j) g(\beta_j; \pi) d\beta_j \\
& = \prod_j \int L(\beta_j) g(\beta_j; \pi) d\beta_j \\
& \approx \prod_j \int \hat{L}(\beta_j) g(\beta_j; \pi) d\beta_j
\end{align}
